### 2017-09-26 TF-vldb2018/sec-appendix.tex

@@

The decision version of the {\em pattern fragmentation} problem, denoted by $\kw{dOFGP}(P, h, r_1, r_2)$,
is to decide whether there exists a fragmentation \{${P}_{f1}$, \ldots, $P_{fh}$, $C$\} such that,
(a) $\max_i |P_{fi}| \leq r_1\cdot\frac{|P|}{h}$ and (b) $|C|\leq r_2|P|$.

@@

\vspace{-2ex}
Given an instance of the minimum cut problem,
we construct an instance of $h$-fragmentation problem.
It can be achieved by taking $H$ as $P$, and setting $h=2$, $r_1=h$ and $r_2 = m/|P|$.
Indeed, the minimum cut problem is a special case of the of $h$-fragmentation problem.

@@

We will prove the proposition by contradiction.
When $\Delta P$ comes, the perfect graphs must reside in the balls that match with each pattern fragment of $P\oplus \Delta P$.
\identifyaffball identifies \affballsx who already match with each fragment of $P$;
Or else, if there exists a fragment $P_{fi}$ of $P$ that an \affballx cannot match,
there must exist an update in $\Delta P$ on $P_{fi}$,
such that the ball may match with the updated fragment $P_{fi}\oplus \Delta P$.
Therefore, \identifyaffball filters out the balls that do not match with a fragment of $P$, and there are no pattern updates on the fragment.

@@

The proof is similar to the one of Proposition~\ref{prop-canaffballs}.
\identifyaffball filters out the balls that cannot match all fragments,	and there are no data updates on the ball.

>>>>

\revise{
Proofs

}

@@

\revise{
The decision version of the {\em pattern fragmentation} problem, denoted by $\kw{dOFGP}(P, h, r_1, r_2)$,
is to decide whether there exists a fragmentation \{${P}_{f1}$, \ldots, $P_{fh}$, $C$\} such that,
(a) $\max_i |P_{fi}| \leq r_1\cdot\frac{|P|}{h}$ and (b) $|C|\leq r_2|P|$.

@@

\vspace{-2ex}
Given an instance of the minimum cut problem,
we construct an instance of $h$-fragmentation problem.
It can be achieved by taking $H$ as $P$, and setting $h=2$, $r_1=h$ and $r_2 = m/|P|$.
Indeed, the minimum cut problem is a special case of the of $h$-fragmentation problem.}

@@

\warn{The proposition is correct as when $\Delta P$ comes, the perfect graphs must reside in the balls that match with each pattern fragment of $P\oplus \Delta P$.}
\identifyaffball identifies \affballsx who already match with each fragment of $P$;
Or else, if there exists a fragment $P_{fi}$ of $P$ that an \affballx cannot match,
there must exist an update in $\Delta P$ on $P_{fi}$,
such that the ball may match with the updated fragment $P_{fi}\oplus \Delta P$.
Therefore, \identifyaffball filters out the balls that do not match with a fragment of $P$, and there are no pattern updates on the fragment.

@@

The proof is similar to the one of Proposition~\ref{prop-canaffballs}.
\identifyaffball filters out the balls that cannot match all $h$ pattern fragments,	and there are no data updates on the ball.
